---
title: "Activity 2"
author: "Narender"
output: github_document
---

```{setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

# Day1 - Activity2

## Task2 : Loading packages
  
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
```


## Task3 :  Loading the data set

```{r}

hfi<-readr::read_csv("https://www.openintro.org/data/csv/hfi.csv",show_col_types = FALSE)

```

**1) The hfi dataset has 1458 observations and 123 variables (1458 * 123). Each row represents data of a country for that specific year**
  
  
  
## filtering the dataframe by year
  
```{r}

hfi_2016 <- hfi %>% filter(hfi$year== 2016)

hfi_new<-hfi_2016 %>% select(pf_expression_control,pf_score)

```

**2) I would use a scatter plot to visualize the relationship between pf_score and pf_expression_control**
  
  
## Plot
  
```{r}
plot1<-hfi_2016 %>% ggplot(aes(x=pf_expression_control,y=pf_score))+
  geom_point(color="red")+
  geom_smooth(method = lm)+
  scale_x_continuous(breaks = c(0,2,4,6,8))+
  scale_y_continuous(breaks = c(0,2,4,6,8))+
  labs(title= "Relationship between pf_score and pf_expression_control",
       x="pf_expression control",
       y="pf_score")+
  theme_bw()


plot1
```

**3) The relationship looks linear and we can predict the pf_score using this linear model when given the pf_expression_control**
  
  
## Task4 : Sum of Squared residuals
  
**4) The smallest sum of square that I have got was 104.954 when compared to other sum of squares (106.075, 112.042, 106.772, 108.213, 118.636) that I got while trying to minimize the sum of squared residuals.**
  
  
## Task5 : Linear model
  
```{r}
m1 <- lm(pf_score ~ pf_expression_control, data = hfi_2016)
tidy(m1)
```

**5) The Y-intercept from the equation was 4.28**
  
**6) The slope from the equation was 0.542**
  
  
  
# Day2 - Activity2
  
## Task2: Overall model fit

```{r}
# Correlation coefficient between pf_expression_control and pf_score

cor_coeff <-cor(hfi_2016$pf_expression_control,hfi_2016$pf_score,use ="everything",method = c("pearson","kendall","spearman"))

cor_coeff
```
**1) The correlation coefficient for this model means how related the pf_expression_control and pf_score are. The correlation coefficient is 0.845**


```{r}
glance(m1)
```

**2) The value of R-square for this model is 0.714**
**3) It explains the proportion of variation in pf_score explained by pf_expression_control**


```{r}
m2 <- lm(hf_score ~ pf_expression_control, data = hfi_2016)
tidy(m2)
```

**4) The Regression line equation was y = 5.05 + 0.37 * pf_expression_control.**

**5) For every 1 unit increase in pf_expression_control, we expect a country’s mean human freedom score to increase 0.368 units.**

## Task3 : Prediction and prediction errors

```{r}
plot1
```

**6) we can use the regression line equation to find the personal freedom score which will be 5.906 for a pf_expression_control rating of 3**

**7) This is an overestimate by 0.44**



## Task 4: Model diagnostics

```{r}
m1_aug <- augment(m1)
```


```{r}
ggplot(data = m1_aug, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  xlab("Fitted values") +
  ylab("Residuals")
```


**8) The points around the red horizantal line are randomly scattered. Since the points show no pattern,  we can say that the linear model is correct.**


```{r}
ggplot(data = m1_aug, aes(x = .resid)) +
  geom_histogram(binwidth = 0.25) +
  xlab("Residuals")
```

**9) By the histogram above we can say that the data voilated the nearly-normal condition, because the histogram is skewed rather than being approximately normal**

**10)Based on the residuals vs fitted plot we can say that the constant variance assumption is not violated because the residuals are scattered with no particular pattern and exhibiting roughly constant variance at each level of fitted values.**
