---
title: "Activity 2 - Day 1"
author: "Narender"
output: github_document
---

```{setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

## Task2 : Loading packages
  
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
```


## Task3 :  Loading the data set

```{r}

hfi<-readr::read_csv("https://www.openintro.org/data/csv/hfi.csv",show_col_types = FALSE)

```

**1) The hfi dataset has 1458 observations and 123 variables (1458 * 123). Each row represents data of a country for that specific year**
  
  
  
## filtering the dataframe by year
  
```{r}

hfi_2016 <- hfi %>% filter(hfi$year== 2016)

```

**2) I would use a scatter plot to visualize the relationship between pf_score and pf_expression_control**
  
  
## Plot
  
```{r}
plot1<-hfi_2016 %>% ggplot(aes(x=pf_expression_control,y=pf_score))+
  geom_point(color="red")+
  geom_smooth(method = lm)+
  scale_x_continuous(breaks = c(0,2,4,6,8))+
  scale_y_continuous(breaks = c(0,2,4,6,8))+
  labs(title= "Relationship between pf_score and pf_expression_control",
       x="pf_expression control",
       y="pf_score")+
  theme_bw()


plot1
```

**3) The relationship looks linear and we can predict the pf_score using this linear model when given the pf_expression_control**
  
  
## Task4 : Sum of Squared residuals
  
**4) The smallest sum of square that I have got was 104.954 when compared to other sum of squares (106.075, 112.042, 106.772, 108.213, 118.636) that I got while trying to minimize the sum of squared residuals.**
  
  
## Task5 : Linear model
  
```{r}
m1 <- lm(pf_score ~ pf_expression_control, data = hfi_2016)
tidy(m1)
```

**5) The Y-intercept from the equation was 4.28**
  
**6) The slope from the equation was 0.542**
  
  
  